Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-09 manuscript/cpcrw_manuscript.Rmd
Outlining results and discussion

* joined with mass data
* flux computation

The GHG concentration measurements for each sample (i.e., each gas, core, and date/time) were used to calculate a linear rate of change (δc/δt), based on the concentration rise from a minimum (at 2-10 seconds after measurement began) to a maximum (at 10-45 seconds). Each core’s respiration flux (F) was then calculated following e.g. Steduto et al. {, 2002 #3383} as $F=\frac{\delta c}{\delta t} \frac{V}{M} \frac{P_a}{RT}$ where V is the core-specific system volume, M the core dry mass as determined at the end of the incubation, Pa atmospheric pressure (101 kPa; the incubation chambers were ~120 m a.s.l.), R the universal gas constant (8.3 x 10^-3^ m^3^ kPa mol^-1^ K^-1^) and T the chamber air temperature (K) at time of measurement. The final respiration rate was expressed as mg C kg soil^-1^ day^-1^. TODO check all units

Q10 computation

* stats

@@

Results.

@@

Discussion.

@@

@@

Acknowledgments.

>>>>

The GHG concentration measurements for each sample (i.e., each gas, core, and date/time) were used to calculate a linear rate of change (δc/δt), based on the concentration rise from a minimum (at 2-10 seconds after measurement began) to a maximum (at 10-45 seconds). Each core’s respiration flux (F) was then calculated following e.g. Steduto et al. {, 2002 #3383} as $F=\frac{\delta c}{\delta t} \frac{V}{M} \frac{P_a}{RT}$ where V is the core-specific system volume, M the core dry mass as determined at the end of the incubation, Pa atmospheric pressure (101 kPa; the incubation chambers were ~120 m a.s.l.), R the universal gas constant (8.3 x 10^-3^ m^3^ kPa mol^-1^ K^-1^) and T the chamber air temperature (K) at time of measurement. The final respiration rate was expressed on a dry soil mass basis (mg C kg soil^-1^ day^-1^). TODO check all units

* joined with mass and ancillary data
* correlations
* Q10 computation
* stats

@@

* Soil WC changes over incubation (Figure 1)

* Gas fluxes over incubation (Figures 2 and 3)
* Statistical tests of WC and temperature on fluxes

* Cumulative fluxes (Figure 4)
* CO2:CH4 ratio
* Statistical tests of WC and temperature on cumulative fluxes

@@

Compare absolute flux rates to other published studies from boreal mineral soils.

@@

Note high CO2:CH4 ratios, compare with Treat et al. and other studies.

Rises in boreal soil temperatures - who has quantified this? Changes in soil WC much less certain. Thermokarst etc., deepening of active layer - that's the larger implications of this work.

@@

This research was supported by Office of Science of the U.S. Department of Energy as part of the Terrestrial Ecosystem Sciences Program. The Pacific Northwest National Laboratory is operated for DOE by Battelle Memorial Institute under contract DE-AC05-76RL01830.
